Data Management Plan

### 2021-11-30 application/dataManagementPlan_long.tex
Added UCL Research Data Management group
Added input from John Pelan

The project collaborator, NeuroGEARS Ltd, and its lead, Dr.~Gon\c{c}alo Lopes, have extended experience of software management and distribution, and will support our efforts.  In addition we will benefit from advice from UCL's recently established Centre for Advanced Research Computing.

>>>>

The project collaborator, NeuroGEARS Ltd, and its lead, Dr.~Gon\c{c}alo Lopes,
have extended experience of software management and distribution, and will
support our efforts.  In addition we will benefit from advice from UCL's
recently established Centre for Advanced Research Computing and the UCL
Research Data Management group. Local storage platforms at the SWC/GCNU, with
more than six peta bytes of space, will be used to mirrow Github repositories.
